%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Senior Software Engineer} % Job title
    {LinkedIn} % Organization
    {San Francisco, CA} % Location
    {February 2022 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed and maintained a data visualization library using Ember.js and Highcharts.js, enabling scalable and interactive charting solutions for LinkedIn Recruiter reports. Drove cross-organizational impact by standardizing charting solutions, improving performance, and enhancing the user experience for data-driven decision-making across LinkedIn’s recruiting ecosystem.}
        \item {Iterated on existing features, write unit tests, improve the user experience and accessibility for LinkedIn recruiter product.} 
        \item {Accessibility champion for the org, lead the effort every annual audit, and drive the implementation, triaging, providing technical while ensuring accessibility best practices to meet Microsoft's accessibility standards.} 
        \item {Built out a natural language interface powered by Generative AI, enabling users to effortlessly query, analyze, and visualize their reporting data to streamline data exploration and enhancing decision-making.}
        \item {Implemented a personalized summary report feature that improved page views by 10\%}
        \item {Mentored a Front end engineering summer intern.}
      \end{cvitems}
    }

  \cventry
    {Lead Front End Engineer - Growth} % Job title
    {Glassdoor} % Organization
    {San Francisco, CA} % Location
    {November 2021 - February 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead the Growth team, drove detailed project definition, design, cross-functional alignment, estimation, in addition to task break-down, delivery, monitoring, and maintenance.}
        \item {Worked closely with product and engineering managers to identify and plan projects based on the team goals and resources and set project direction for my two direct reports. Implementation, roll-out and maintenance of projects.}
        \item {Took part in the hiring process conducting technical interviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Front End Engineer - Traffic \& Growth} % Job title
    { } % Organization
    { } % Location
    {December 2019 - November 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed custom AD templates and built out new employer branding features using React that help employers attract talent on Glassdoor.}
        \item {Developed an analytics dashboard using Highcharts that provides employers insights into their ad campaigns.}
        \item {Developed a SEO library for Node.js SSR apps to abstract SEO best practices (such as title, meta, ldjson, hreflang and canonicals) and generate SEO links for several international domains which helps Glassdoor's pages rank consistently high in Google's search results.}
        \item {Refactored the job alerts front end library to use React Hooks and emotion, reduced bundle size by 33\%. Over 10k job alerts are created daily using this interface.}
        \item {Prototyped and launched several A/B tests across the consumer site on Glassdoor.com to drive user growth. Achieved an \textasciitilde50\% increase in content contributions on Glassdoor to date with the content hard-sell feature.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Software Developer Level II} % Job title
    {Fujifilm North America Corporation} % Organization
    {Rochester, NY} % Location
    {October 2015 - December 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {As a Lead engineer, provide software engineering expertise through various stages of agile SDLC. Mentor junior developers through code reviews and paired programming efforts. Follow emerging standards and best practices for software development architecture and tooling, prototype and refine new business ideas, and learn new technologies as needed.}
        \item {Developed a kiosk photo printing solution using Vue.js, Bootstrap and Node.js Restful services. Lowered cost by optimizing performance on cheaper hardware. Improved UX by reducing the time between checkout and printing by 30\% by restructuring the ordering workflow.}
        \item {Leveraged Lottie - an animation library to repurpose visually stunning and engaging animations created using Adobe After Effects in the kiosk's UI with minimal development effort which increased CTR by at least 20\%.}
        \item {Built a mobile-first responsive design website using ASP.NET Core, Bootstrap and jQuery for customers to order personalized photo products.}
        \item {Increased web traffic by \textasciitilde35\% by generating personalized 3D renders of products with user's images for an upsell section on a landing page.}
       % \item {Improved brand identity across several products by refactoring styles to use Sass to achieve a more uniform and consistent design.}
        \item {Improved the checkout experience and increased order conversion rates by at least 10\% in several products across mobile and web by integrating with third-party payment processors such as PayPal and Square.}
       % \item{Reduced webpage load times by up to 25\% by using Webpack to optimize images, bundle Javascript and CSS in a production environment.}
        \item {Updated backend services and architecture to streamline promotion offerings across e-commerce apps and improve reporting.}
        \item {Developed a wireless \href{https://play.google.com/store/apps/details?id=com.fujifilm.wifi}{photo transfer app} for Android and iOS. Achieved \textasciitilde95\% device penetration. Currently ranked at 38, previously featured in the top 10 free photography apps in the \href{https://play.google.com/store/apps/category/PHOTOGRAPHY/collection/topselling_free}{Google Play Store} over a 12 month period.}
        \item {Collaborated with a wireless carrier to integrate Fujifilm’s photo ordering SDK into their Cloud app thereby increasing revenue 100\% YOY.}
        %\item {Setup repositories for modern package managers like Nuget and npm to host internal software packages, thereby promoting code reuse, cross-team collaboration and reduced redundancy across teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer Level I} % Job title
    { } % Organization
    { } % Location
    {September 2012 - February 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Developed photo editors for multi-page products using HTML5, CSS3, and Backbone.js used in over 15,000 kiosks that are available at 10,000+ retail locations across North America. Leveraged an image ranking algorithm to build an auto-fill feature for multi-page products.}
    \item{\href{https://www.fujifilmapi.com}{Developed an SDK for} creating and ordering personalized photo products for Android and iOS that has over 500 integrations, allowing users to order from a catalog of 180+ products.}
    %\item {Part of Fujifilm's five-person team for Photo Hack Day 4, a weekend-long coding hackathon at Facebook HQ.}
      \end{cvitems}
    }

%---------------------------------------------------------
  %\cventry
   % {Software Developer Coop} % Job title
   % { } % Organization
   % { } % Location
   % {January 2012 - June 2012} % Date(s)
  %  {
     % \begin{cvitems} % Description(s) of tasks/responsibilities
    %    \item {Saved hundreds of billable hours by developing a service backed by a message queue to automatically update and sync photo product catalogs.}
    %    \item{Prototyped a JSON serialization library due to the lack of support in iOS4, developed an SDK for a Restful service for quick and easy integrations.}
    %    \item {Designed email templates for order status notifications and updates used in all e-commerce apps.}
     % \end{cvitems}
   % }

%---------------------------------------------------------
  %\cventry
   % {Software Engineering Coop} % Job title
   % {IDI Billing Solutions} % Organization
    %{Victor, NY} % Location
   % {December 2010 - May 2011} % Date(s)
   % {
    %  \begin{cvitems} % Description(s) of tasks/responsibilities
     %   \item {Provided user requirements analysis, design and development support for enhancement of a telecommunication billing SAAS product.}
     % \end{cvitems}
   % }

%---------------------------------------------------------
\end{cventries}
